The SNIK Ontology of Hospital Information Management

### 2019-03-01 paper.tex
Add references and extend structure.

\begin{abstract}
Abstract text.
\end{abstract}

@@

\section{Background}
\todo{not Konrad: write background of meta model}

\section{Architecture}
The \textbf{Semantic Network of Information Management in Hospitals} (\enquote{Krankenhaus} in German) is an OWL 2 DL ontology that consists of a central meta model and modular subontologies based on the meta model.

\section{Data Set Description}

\section{Application}

>>>>

\begin{abstract}
This paper describes the ontology of the \textbf{Semantic Network of Information Management in Hospitals} (SNIK).  
\end{abstract}

@@

\section{Background}\label{sec:background}
\todo{not Konrad: write background of meta model}
\citet{domaene} contains an initial structure of the meta model.

\section{Architecture}\label{sec:architecture}
\todo{Describe the meta model here}
The \textbf{Semantic Network of Information Management in Hospitals} (\enquote{Krankenhaus} in German) is an OWL 2 DL ontology that consists of a central meta model and modular subontologies based on the meta model.

\section{Data Set Description}\label{sec:dsd}
The SNIK ontologies are available at \url{http://www.snik.eu/ontology/} under the Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International license.
The SNIK ontologies contain knowledge about information management in hospitals from three textbooks, an interview and a standard.
- Blue Book~\citep{bb}
- Orange Book~\citep{ob}
- CIOX
- Heinrich~\citep{he}
- IT4IT

\section{Application}\label{sec:application}
The SNIK ontologies were initially intended as the basis for a decision support system for hospital CIOs~\citep{domaene}.
While such a system was designed and a prototype was implemented, it was ultimately not integrated into the informational infrastructure of the Unilklinikum Leipzig.

- verweis auf existierende papers
